Coherent optical association of a single molecule

### 2020-11-04 paper.tex
Update on Overleaf.
White space, regenerate PDF
Fix latex and revtex warning

\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{footmisc}
\usepackage{braket}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\mathrm{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

  %that also has the advantage of having a reduced sensitivity
  %to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
  %This reduces the intensity stability requirement to $5\%$
  %instead of $0.3\%$ which is typical for other states.

@@

In additional to calibrating the $\Omega_m$ and $\Omega_a$,
the scattering rate of the molecule depends on the tweezer power and detuning.
At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
However, since the technical noise that can lead to decoherence
is not fully characterized in our experiment,
we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
%the discrepancy based on the dependency.

@@

\begin{acknowledgments}
  We would like to thank Bo Gao and Paul Julienne, Rosario (?) (anybody else) for discussion. This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation. J.~T.~Z. is supported by a National Defense Science and Engineering Graduate Fellowship. W.~C. is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship. K.~W. is supported by an NSF GRFP fellowship. J.~M.~H. is supported by the U.K. Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
\end{acknowledgments}

>>>>

\documentclass[aps,prl,twocolumn,10pt,superscriptaddress]{revtex4-1}
% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage[utf8x]{inputenc}
\usepackage[colorlinks=true]{hyperref}
\usepackage{footmisc}
\usepackage{braket}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematics of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $c^3\Sigma$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

@@

% that also has the advantage of having a reduced sensitivity
% to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
% This reduces the intensity stability requirement to $5\%$
% instead of $0.3\%$ which is typical for other states.

@@

In additional to calibrating the $\Omega_m$ and $\Omega_a$,
the scattering rate of the molecule depends on the tweezer power and detuning.
At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
However, since the technical noise that can lead to decoherence
is not fully characterized in our experiment,
we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
% the discrepancy based on the dependency.

@@

\begin{acknowledgments}
  We would like to thank Bo Gao,  Paul Julienne, and Rosario Gonzalez-Ferez for discussion. This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation. J.~T.~Z. is supported by a National Defense Science and Engineering Graduate Fellowship. W.~C. is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship. K.~W. is supported by an NSF GRFP fellowship. J.~M.~H. is supported by the U.K. Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
\end{acknowledgments}
